Title

### 2013-03-05 inc/extension/external_forces/external_forces.tex
consistent use of v_max vs v_0

To specify the physical region of influence of the lenses, it is convenient to redefine $M_{i}$ to include a super-Gaussian envelope in $z^{\prime}$, the position of the peak of the pulse in the lab frame;
\begin{equation} \label{eq:reg_of_influence}
  M_{i}	\to M_{i} \exp \left [ - \left (  \frac{ z^{\prime} - z_{lens}^{\prime} }{ L_{lens} / 2 } \right )^{ 2 n } \right ] \text{ ,}
\end{equation}
where $z_{lens}^{\prime}$ is the position of the center of the lens, $L_{lens}$ is the length of the lens and $n$ is the super-Gaussian order parameter.
The order parameter defines the ``sharpness'' of the edge of the region of influence with integer values ranging from 1 (a simple Gaussian) through $\infty$ (a top-hat).
We connect $z^{\prime}$ to $t$ through $ v_{{ \scriptscriptstyle 0}} $; the kinetic equations are simply defined for the position of the peak of the pulse.

@@

The spatial dependence of the axial RF electric field experienced by the electron pulse in a TM$_{010}$ cavity of radius $a$ may be written as
\begin{equation} \label{eq:RF_Efield}
  E ( r , z , z^{\prime} ) = E_{0} \sin \left ( \frac{ \Omega ( z^{\prime} - z ) }{ v_{{ \scriptscriptstyle 0}} } + \phi \right )\operatorname{J_{0}} \left ( \frac{ k r }{ a } \right ) \text{,}
\end{equation}
where $ E_{ 0 } $ is the oscillating field amplitude, $\Omega$ is the RF frequency and $\phi$ is a phase factor determining whether the RF cavity acts as a pulse compressor $ ( \phi \approx 0 ) $ or an electron accelerator $ ( \phi \approx \pm \pi/2 ) $.
The coordinate $z^{\prime} $ describes the position of the center of the pulse in the RF cavity, which extends from $ z^{\prime} = - d / 2 $ to $ z^{\prime} = d / 2 $, and $z$ is the position of any electron in the pulse with respect to the center of the pulse.
For the $\text{TM}_{010}$ oscillation mode, the RF frequency is given by
\begin{equation}
  \Omega = \frac{ c k }{a} \text{,}
\end{equation}
where $c$ is the speed of light in a vacuum and $ k = 2.405 $ is the first zero of the $\operatorname{ J_{0} }$ Bessel function.

For the usual case of a spatially compact electron pulse with respect to the dimension of the RF cavity (i.e., $ \Omega z \ll v_{{ \scriptscriptstyle 0}} $ and $ \sqrt{\sigma_{\smallT}} \ll a $), \ref{eq:RF_Efield} can be rewritten as
\begin{equation} \label{eq:RF_Efield_approx}
  E ( r , z , z^{\prime} ) = E_{0} \biggl [ \sin \left ( \frac{ \Omega z^{\prime} }{ v_{{ \scriptscriptstyle 0}} } + \phi \right ) - \frac{ \Omega z }{ v_{{ \scriptscriptstyle 0}} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{{ \scriptscriptstyle 0}} } + \phi \right ) \biggr ] \text{,}
\end{equation}
which demonstrates that the RF cavity acts both as a pulse acceleration (first term on RHS of \ref{eq:RF_Efield_approx}) and a pulse compression or expansion (second term on RHS of \eqref{eq:RF_Efield_approx}) device.
The second term then gives the desired form (see \ref{eq:linear_force}) for the force manipulating the temporal dynamics and characteristics during electron pulse compression;
\begin{equation} \label{eq:RF_Force_z}
  \boldsymbol{F}_{ z , RF } = - \left [ \frac{ e \Omega E_{0} }{ v_{{ \scriptscriptstyle 0}} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{{ \scriptscriptstyle 0}} } + \phi \right ) \right ] z \hat{\operatorname{ \boldsymbol{z} }} \text{.}
\end{equation}

By considering the impulse exerted by the RF cavity field on the electrons in the pulse, it is straightforward to show that pulse compression (when $\phi = 0$) is maximized for $ \Omega d / (2 v_{{ \scriptscriptstyle 0}} ) = \pi /2 $; that is, the time of flight of the electron pulse through the RF cavity of length $ d $ is equal to half the RF period.
Such a calculation assumes that the pulse velocity $v_{{ \scriptscriptstyle 0}}$ is constant; so that, the condition that $ \phi = 0 $ when the pulse is at the center of the RF cavity (i.e., when the pulse is at $ z^{\prime} = 0 $) is readily met.
As suggested by the acceleration term in \ref{eq:RF_Efield_approx}, this is only a good approximation if the RF field amplitude $E_{0}$ is sufficiently small to not affect the velocity of the peak of the pulse as it propagates through the cavity.
As a result, in practice, the phase $\phi$ of the RF field is adjusted to optimize the performance of the cavity.

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $,\cite{kim_rf_1989} where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures, as illustrated by $1 \frac{1}{2}$-cell RF photo-gun designs.\cite{mcdonald_design_1988}
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{{ \scriptscriptstyle 0}} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{{ \scriptscriptstyle 0}} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{{ \scriptscriptstyle 0}} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
For the examples shown below under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{{\scriptscriptstyle 0}} / \Omega $,\cite{kim_rf_1989} even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

>>>>

To specify the physical region of influence of the lenses, it is convenient to redefine $M_{i}$ to include a super-Gaussian envelope in $z^{\prime}$, the position of the peak of the pulse in the lab frame;
\begin{equation} \label{eq:reg_of_influence}
  M_{i}	\to M_{i} \exp \left [ - \left (  \frac{ z^{\prime} - z_{lens}^{\prime} }{ L_{lens} / 2 } \right )^{ 2 n } \right ] \text{ ,}
\end{equation}
where $z_{lens}^{\prime}$ is the position of the center of the lens, $L_{lens}$ is the length of the lens and $n$ is the super-Gaussian order parameter.
The order parameter defines the ``sharpness'' of the edge of the region of influence with integer values ranging from 1 (a simple Gaussian) through $\infty$ (a top-hat).
We connect $z^{\prime}$ to $t$ through $ v_{\smallzero} $; the kinetic equations are simply defined for the position of the peak of the pulse.

@@

The spatial dependence of the axial RF electric field experienced by the electron pulse in a TM$_{010}$ cavity of radius $a$ may be written as
\begin{equation} \label{eq:RF_Efield}
  E ( r , z , z^{\prime} ) = E_{0} \sin \left ( \frac{ \Omega ( z^{\prime} - z ) }{ v_{\smallzero} } + \phi \right )\operatorname{J_{0}} \left ( \frac{ k r }{ a } \right ) \text{,}
\end{equation}
where $ E_{ 0 } $ is the oscillating field amplitude, $\Omega$ is the RF frequency and $\phi$ is a phase factor determining whether the RF cavity acts as a pulse compressor $ ( \phi \approx 0 ) $ or an electron accelerator $ ( \phi \approx \pm \pi/2 ) $.
The coordinate $z^{\prime} $ describes the position of the center of the pulse in the RF cavity, which extends from $ z^{\prime} = - d / 2 $ to $ z^{\prime} = d / 2 $, and $z$ is the position of any electron in the pulse with respect to the center of the pulse.
For the $\text{TM}_{010}$ oscillation mode, the RF frequency is given by
\begin{equation}
  \Omega = \frac{ c k }{a} \text{,}
\end{equation}
where $c$ is the speed of light in a vacuum and $ k = 2.405 $ is the first zero of the $\operatorname{ J_{0} }$ Bessel function.

For the usual case of a spatially compact electron pulse with respect to the dimension of the RF cavity (i.e., $ \Omega z \ll v_{\smallzero} $ and $ \sqrt{\sigma_{\smallT}} \ll a $), \ref{eq:RF_Efield} can be rewritten as
\begin{equation} \label{eq:RF_Efield_approx}
  E ( r , z , z^{\prime} ) = E_{0} \biggl [ \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) - \frac{ \Omega z }{ v_{\smallzero} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \biggr ] \text{,}
\end{equation}
which demonstrates that the RF cavity acts both as a pulse acceleration (first term on RHS of \ref{eq:RF_Efield_approx}) and a pulse compression or expansion (second term on RHS of \eqref{eq:RF_Efield_approx}) device.
The second term then gives the desired form (see \ref{eq:linear_force}) for the force manipulating the temporal dynamics and characteristics during electron pulse compression;
\begin{equation} \label{eq:RF_Force_z}
  \boldsymbol{F}_{ z , RF } = - \left [ \frac{ e \Omega E_{0} }{ v_{\smallzero} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \right ] z \hat{\operatorname{ \boldsymbol{z} }} \text{.}
\end{equation}

By considering the impulse exerted by the RF cavity field on the electrons in the pulse, it is straightforward to show that pulse compression (when $\phi = 0$) is maximized for $ \Omega d / (2 v_{\smallzero} ) = \pi /2 $; that is, the time of flight of the electron pulse through the RF cavity of length $ d $ is equal to half the RF period.
Such a calculation assumes that the pulse velocity $v_{\smallzero}$ is constant; so that, the condition that $ \phi = 0 $ when the pulse is at the center of the RF cavity (i.e., when the pulse is at $ z^{\prime} = 0 $) is readily met.
As suggested by the acceleration term in \ref{eq:RF_Efield_approx}, this is only a good approximation if the RF field amplitude $E_{0}$ is sufficiently small to not affect the velocity of the peak of the pulse as it propagates through the cavity.
As a result, in practice, the phase $\phi$ of the RF field is adjusted to optimize the performance of the cavity.

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $,\cite{kim_rf_1989} where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures, as illustrated by $1 \frac{1}{2}$-cell RF photo-gun designs.\cite{mcdonald_design_1988}
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
For the examples shown below under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $,\cite{kim_rf_1989} even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

### 2013-03-05 inc/extension/initial_conditions/initial_conditions.tex
consistent use of v_max vs v_0

% longitudinal
In the longitudinal direction ($z$), the interplay between acceleration, $ a = e E_{DC}/m $, in the DC gun and the physics of the photoemission process determine the initial values of $\sigma_z$, the longitudinal spatial variance, and $\gamma_z$, the longitudinal momentum chirp, of an electron bunch.
Two limiting regimes for the initial longitudinal variances $ \sigma_{i} ( 0 ) $ are readily identified: (i) when the incident drive laser pulse duration is sufficently long to ensure that the distance the electrons travel due to acceleration in $ E_{DC} $ over the laser pulse duration is much greater than the distance traveled by electrons moving with a constant velocity $ v_{0} = \sqrt{ 2 \Delta E / m } $, the maximum photoemission velocity, over the same time period; and (ii) the opposite regime for sufficiently short laser pulse durations.

@@

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
Since the electric field has no time to influence the front of the pulse before the back is also generated we can say that the front of the pulse has a velocity equal to $v_0$ and the back is essentially stationary just after generation.
Further, since the photoemission efficiency is proportional to $\Delta E^2$ \cite{shalaev_electron_1994} the distribution of emitted electrons vs velocity is proportional to $v^4$; therefore to a first approximation it is reasonable to say that in this case $\Delta v \approx v_0$.
The pulse's initial spatial variance $\Delta z$ is therefore approximately to the spread of distances traveled during the laser pulse duration $\Delta t_L$,
\begin{equation} 
  \sqrt{ \sigma_{ z } ( 0 ) } \approx \Delta z = \Delta v \Delta t_{L} = \frac{ v_{ 0 } \tau }{ \sqrt{ 2 } } \punct{.}
\end{equation}
Once again, we can use this information to determine a velocity chirp across the pulse in this regime,
\begin{equation}
  \gamma_{ z } ( 0 ) \approx m \Delta v \Delta z = m v_{ 0 } \sqrt{ \sigma_{ z } ( 0 ) } \punct{,}
\end{equation}

For simplicity of use, one may combine the initial conditions resulting from these two cases.
Since they arise from independent processes, the initial spatial uncertainties $\sigma_{ z } ( 0 )$ may be added naively 
\begin{equation} \label{eq:initial_sigma_z}
  \sigma_{ z } ( 0 ) \approx \frac{ ( v_{ 0 } \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \punct{.}
\end{equation}
In the case of the initial momentum chirp terms $\gamma_{ z } ( 0 )$, while it is perhaps more rigorously correct to naively add  the terms with the spatial variance evaluated in each respective limit, we propose that the evaluation be done in terms of the resultant form presented in \ref{eq:initial_sigma_z}, keeping $\sigma_{z}$ unevaluated, 
\begin{equation}
  \gamma_{ z } ( 0 ) \approx \sqrt{ \sigma_{ z } ( 0 ) } \left ( m v_{ 0 } + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \punct{.}
\end{equation}
In this way the model may, in an intermediate case, more closely reflect the pulse length as modeled rather than the pulse length as idealized in each limiting case.

@@

In conclusion, the resulting set of analytic initial conditions for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form} are
\begin{subequations} \label{eq:summary}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) \approx \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) \approx \frac{ ( v_{ 0 } \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) \approx 0 \\
    \gamma_{ z } ( 0 ) \approx \sqrt{ \sigma_{ z } ( 0 ) } \left ( m v_{ 0 } + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \\
    \eta_{ z } ( 0 ) \approx \frac{ \eta_{ \smallT } ( 0 ) }{ 4 } \punct{.}
  \end{gather}
\end{subequations}
Unless otherwise noted, these initial conditions will be used in all simulations for the remainder of this paper.

@@

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_0 N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the inital photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{ 0 } $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to seperate from one another.

>>>>

% longitudinal
In the longitudinal direction ($z$), the interplay between acceleration, $ a = e E_{DC}/m $, in the DC gun and the physics of the photoemission process determine the initial values of $\sigma_z$, the longitudinal spatial variance, and $\gamma_z$, the longitudinal momentum chirp, of an electron bunch.
Two limiting regimes for the initial longitudinal variances $ \sigma_{i} ( 0 ) $ are readily identified: (i) when the incident drive laser pulse duration is sufficently long to ensure that the distance the electrons travel due to acceleration in $ E_{DC} $ over the laser pulse duration is much greater than the distance traveled by electrons moving with a constant velocity $ v_{max} = \sqrt{ 2 \Delta E / m } $, the maximum photoemission velocity, over the same time period; and (ii) the opposite regime for sufficiently short laser pulse durations.

@@

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
Since the electric field has no time to influence the front of the pulse before the back is also generated we can say that the front of the pulse has a velocity equal to $v_{max}$ and the back is essentially stationary just after generation.
Further, since the photoemission efficiency is proportional to $\Delta E^2$ \cite{shalaev_electron_1994} the distribution of emitted electrons vs velocity is proportional to $v^4$; therefore to a first approximation it is reasonable to say that in this case $\Delta v \approx v_{max}$.
The pulse's initial spatial variance $\Delta z$ is therefore approximately to the spread of distances traveled during the laser pulse duration $\Delta t_L$,
\begin{equation} 
  \sqrt{ \sigma_{ z } ( 0 ) } \approx \Delta z = \Delta v \Delta t_{L} = \frac{ v_{max} \tau }{ \sqrt{ 2 } } \punct{.}
\end{equation}
Once again, we can use this information to determine a velocity chirp across the pulse in this regime,
\begin{equation}
  \gamma_{ z } ( 0 ) \approx m \Delta v \Delta z = m v_{max} \sqrt{ \sigma_{ z } ( 0 ) } \punct{,}
\end{equation}

For simplicity of use, one may combine the initial conditions resulting from these two cases.
Since they arise from independent processes, the initial spatial uncertainties $\sigma_{ z } ( 0 )$ may be added naively 
\begin{equation} \label{eq:initial_sigma_z}
  \sigma_{ z } ( 0 ) \approx \frac{ ( v_{max} \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \punct{.}
\end{equation}
In the case of the initial momentum chirp terms $\gamma_{ z } ( 0 )$, while it is perhaps more rigorously correct to naively add  the terms with the spatial variance evaluated in each respective limit, we propose that the evaluation be done in terms of the resultant form presented in \ref{eq:initial_sigma_z}, keeping $\sigma_{z}$ unevaluated, 
\begin{equation}
  \gamma_{ z } ( 0 ) \approx \sqrt{ \sigma_{ z } ( 0 ) } \left ( m v_{max} + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \punct{.}
\end{equation}
In this way the model may, in an intermediate case, more closely reflect the pulse length as modeled rather than the pulse length as idealized in each limiting case.

@@

In conclusion, the resulting set of analytic initial conditions for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form} are
\begin{subequations} \label{eq:summary}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) \approx \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) \approx \frac{ ( v_{max} \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) \approx 0 \\
    \gamma_{ z } ( 0 ) \approx \sqrt{ \sigma_{ z } ( 0 ) } \left ( m v_{max} + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \\
    \eta_{ z } ( 0 ) \approx \frac{ \eta_{ \smallT } ( 0 ) }{ 4 } \punct{.}
  \end{gather}
\end{subequations}
Unless otherwise noted, these initial conditions will be used in all simulations for the remainder of this paper.

@@

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_{max}N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the inital photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{max} $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to seperate from one another.

### 2013-03-05 inc/model_results/shapes/shapes.tex
consistent use of v_max vs v_0

The initial `space-time' eccentricity \ref{eq:define_xi}, $\xi ( 0 ) = v_{{ \scriptscriptstyle 0}} \tau / w $ , of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \sigma_{ \smallT }(0) = \sigma_{z} ( 0 ) $), `disk-like' ($ \sigma_{ \smallT } ( 0 ) > \sigma_{ z } ( 0 ) $), and `cigar-like' ($ \sigma_{ z } ( 0 ) > \sigma_{ \smallT } ( 0 ) $) pulses.
%TODO rewrite using w?
For simplicity, and unlike most simulations in this paper, the pulses in this simulation are not calculated from laser and photocathode parameters, but are rather defined directly.
The initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ while in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Since the initial pulse volumn is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} ($ N = 10^{6} $ electrons in the bunch) than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} ($ N = 10^{0} $).
The pulse velocity is $ v_{{ \scriptscriptstyle 0}} \approx c/3 $, i.e. a DC photogun with $V = 30\text{kV} $.

>>>>

The initial `space-time' eccentricity \ref{eq:define_xi}, $\xi ( 0 ) = v_{\smallzero} \tau / w $ , of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \sigma_{ \smallT }(0) = \sigma_{z} ( 0 ) $), `disk-like' ($ \sigma_{ \smallT } ( 0 ) > \sigma_{ z } ( 0 ) $), and `cigar-like' ($ \sigma_{ z } ( 0 ) > \sigma_{ \smallT } ( 0 ) $) pulses.
%TODO rewrite using w?
For simplicity, and unlike most simulations in this paper, the pulses in this simulation are not calculated from laser and photocathode parameters, but are rather defined directly.
The initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ while in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Since the initial pulse volumn is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} ($ N = 10^{6} $ electrons in the bunch) than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} ($ N = 10^{0} $).
The pulse velocity is $ v_{\smallzero} \approx c/3 $, i.e. a DC photogun with $V = 30\text{kV} $.
